Verifying Demonstrations

### 2021-06-16 paper/protest-model.tex
Fixes typo and clarifies in protest definitions

%\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every weekend for a few weeks.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the cause,\label{CauseIsTheCommonDenominator} while the location (or area) considered varies over time.

For the rest of the paper, we will refer to the organizer as Alice.
We assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul} %\sonja{commented out for
  %repetition: %\footnote{Note that the objective does not necessarily
              %align with the definition of the police whose interest
              %could be to determine the maximum crowd at any point in
              %time to deploy enough personnel for crowd-control.
%}.
% cause identifier
Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
More specifically, we will use the following definition.
% protest
% subprotest

>>>>

%\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every weekend for a few weeks.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the 
cause,\label{CauseIsTheCommonDenominator} while the location (or area) 
considered varies over several intervals of time.

For the rest of the paper, we will refer to the organizer as Alice.
We assume that the objective of Alice is to count everyone who participated at 
any time and in any of the locations~\cite{2016DemonstrationsInSeoul}. 
%\sonja{commented out for
  %repetition: %\footnote{Note that the objective does not necessarily
              %align with the definition of the police whose interest
              %could be to determine the maximum crowd at any point in
              %time to deploy enough personnel for crowd-control.
%}.
% cause identifier
Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
More specifically, we will use the following definition.
% protest
% subprotest
